Final Presenation

### 2023-04-16 Final Presentation.Rmd
help

---
title: "Final Presenation"
author: "Siddhi Narayan"
date: "2023-04-16"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

## 
table

## Cumulative: Killer Plot
<iframe src="http://127.0.0.1:4571/" width="100%"></iframe>
# Analysis

>>>>

---
title: "Final Presenation"
author: "Siddhi Narayan"
date: "2023-04-16"
output: 
  ioslides_presentation:
    widescreen: true
    css: style.css
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 8, out.width = "100%")
```

@@

## 
table
---
## Cumulative: Killer Plot
```{r, echo= FALSE, message= FALSE}
source("shiny_plot_setup.R")

# Define UI for application that draws a histogram
shinyUI(fluidPage(

    # Application title
    titlePanel("Citation Breakdown by District"),

    # Sidebar with a slider input for number of bins
    sidebarLayout(
        sidebarPanel(
          sliderInput("districts", "District:",
                      min = 1, max = 24,
                      value = 1, step = 1)
        ),

        # Show a plot of the generated distribution
        mainPanel(
            plotOutput("killerplot")
        )
    )
))
#<iframe src="http://127.0.0.1:4571/" width="100%" height="500px"></iframe>
```
# Analysis
